An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-10-03 paper/main.tex
fix refenrece

\bibitem{eMoflon}
  Erhan Leblebici, Anthony Anjorin, and Andy Sch"{u}rr. Developing eMoflon with eMoflon. In Davide Di Ruscio and Daniel Varr´o, editors, Theory and Practice of Model Transformations - 7th International Conference, ICMT 2014, Held as Part of STAF 2014, York, UK, 2014. Proceedings, volume 8568 of Lecture Notes in
Computer Science, pages 138–145. Springer, 2014.

>>>>

\bibitem{eMoflon}
  Erhan Leblebici, Anthony Anjorin, and Andy Sch"{u}rr. Developing eMoflon with eMoflon. In Davide Di Ruscio and Daniel Varro, editors, Theory and Practice of Model Transformations - 7th International Conference, ICMT 2014, Held as Part of STAF 2014, York, UK, 2014. Proceedings, volume 8568 of Lecture Notes in
Computer Science, pages 138–145. Springer, 2014.
